Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-05 PaperMagneticProfiles_JBSMSE.tex
Improved conclusions.
The paragraphs were made more clear, and some numerical results are cited.

To the authors' knowledge, this is the first study where magnetic profiles for AMR model are mathematically modeled and the model parameters are changed in a systematic way. The instantaneous (square wave), rectified cosine and ramp magnetic profiles were implemented in an AMR model, and the profile parameters were varied simultaneously with the regenerator geometric parameters. These waveforms can be found in existing MR devices published in the literature.

Using a simplified model, the instantaneous profile resulted in a higher cooling capacity, even by reducing the blow fraction on rectified cosine, at least up to levels achieved by pumping and valving systems; further reductions of the blow fraction is mainly restricted by valve opening times. This means that, even if sinusoidal profiles can be obtained with more compact magnetic circuit systems, the performance of magnetic refrigeration systems can be maximized by using instantaneous variations of the magnetic field, and then optimizing the regenerator height and blow duration. \colorbox{yellow}{Fabio, tive dificuldade em entender o que voce quis concluir neste paragrafo... talvez seja uma boa tentar expandir seu conteudo}

The ramp profile is a feasible approximation for the instantaneous profile without abrupt changes in the magnetic field plateaus. This waveform can be optimized for increasing cooling capacity, in particular by synchronizing the plateau durations between fluid and magnetic profiles. \colorbox{yellow}{Fabio, acho que seria bom trazer alguns dados quantitativos para ca, tipo ganhos percentuais etc.}

>>>>

To the authors' knowledge, this is the first study where magnetic and fluid flow profiles for an AMR model are mathematically modeled and the model parameters are changed in an integrated and systematic  way. The instantaneous (square wave), rectified cosine and ramp magnetic profiles were implemented in an AMR model, together with an instantaneous fluid flow profile, and the profile parameters were varied simultaneously with the regenerator geometric parameters. These waveforms can be found in existing MR devices published in the literature. A valve model was also incorporated into a more realistic computation of the coefficient of performance.

When comparing the instantaneous  and the rectified cosing magnetic profiles, the cooling capacity associated with the former can be almost \SI{200}{\percent} higher than with the latter, for the same utilization and average high magnetic field and considering optimal blow fractions. The rectified cosing profile suffers from high values of the low magnetic field, and reduction of blow fraction up to the minimum tested value of \SI{60}{\percent} is not enough to overcome the loss in cooling capacity resulting from this effect.

An analysis of power contributions showed that the cost of the higher cooling capacity for the instantaneous profile is a higher valve power associated with the longer blow duration, dominating the other contributions. However, the coefficient of performance is still higher for the square wave. Hence, even though sinusoidal waveforms can be obtained with more compact systems, step-like variations of high amplitude of the magnetic field are preferred if performance is more critical.

The ramp magnetic profile is a feasible approximation for the instantaneous profile without abrupt changes in the magnetic field plateaus. For an AMR device operating with this  profile and the instantaneous fluid flow profile, both cooling capacity and coefficient of performance are maximized if the blow duration is equal to the period of constant magnetic field; if this exact synchronization is not possible, making the magnetization plateau wider than the flow plateau results in smaller reduction of the performance metrics than if it is narrower.

With this strategy and using average values of utilization, it is possible to achieve second-law efficiency levels compatible with vapor-compression systems. Hence the ramp magnetic profile is identified as a suitable target profile in the design of magnetic circuits for AMR devices.
